---
title: "x2 significant results"
author: "Jessica Spencer"
date: "2/24/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("cleaning_for_numerics.R")
#source("cleaning_for_numerics.R")
#code to create table like in Qualtrics
make_table = function(tab,title){
  cont_tab = ftable(tab)
  prop_tab = ftable(round(prop.table(tab)*100, 3))
  #make this an IF to account for times where you can use Chi^2
  fish_test_p = round(fisher.test(tab,simulate.p.value = TRUE, B = 10000)$p.value,4)
  fish_row = c("Fisher's Exact Test Statistic: ",fish_test_p)
  print(title)
  print(cont_tab)
  print(prop_tab)
  fish_row
}

make_table_chi = function(tab,title){
  cont_tab = ftable(tab)
  prop_tab = ftable(round(prop.table(tab,2)*100, 3))
  print(title)
  print(paste("Contingency Table for ",title))
  print(cont_tab)
  print(paste("Contingency Table in Percent of Gender for ",title))
  print(prop_tab)
  print(chisq.test(tab))
}

master_chi_instrument = function(colStart,colEnd,df,gender_column){
  for(i in colStart:colEnd) {       # for-loop over columns
    if(length(unique(df[,i]))>1){
       g= table(df[,i],df$bucketed_gender)
      
      rownames(g) = c("No","Yes")
      title = paste( "Q: Do you play ", names(df)[i] ," at a professional level?")
      make_table_chi(g, title)
    }
   
  }
}

```

#Gender and Tour History

Q14: Are you currently touring or have you toured in the past?

Is gender independent from tour history?

```{r echo=FALSE}
g_t.ever = table(clean_dat$tour.ever,clean_dat$bucketed_gender)
rownames(g_t.ever)=c("Yes","No")
make_table_chi(g_t.ever, "Q14: Are you currently touring or have you toured in the past?")
```
The Chi-Squared test generated a p-value less than 0.5, meaning that the null hypothesis can be rejected. There is a statistically significant relationship between gender and whether or not the participant is touring/has toured in the past.


#Gender and Composer

Q: Is gender independent from the decision to become a composer?

```{r echo=FALSE}
g_compose = table(clean_dat$composer,clean_dat$bucketed_gender) 
rownames(g_compose)=c("Yes","No")
make_table_chi(g_compose, "Q: Are you a composer?")
```
Yes.The Chi-Squared test generated a p-value less than 0.5, meaning that the null hypothesis can be rejected. There is a statistically significant relationship between gender and whether or not the participant is a composer.

#Gender and Arranger
```{r echo=FALSE}
g_arrange = table(clean_dat$arranger,clean_dat$bucketed_gender) 
rownames(g_arrange)=c("Yes","No")
make_table_chi(g_arrange, "Q: Are you an arranger?")
```
Yes. The Chi-Squared test generated a p-value less than 0.05, meaning that the null hypothesis can be rejected. There is a statistically significant relationship between gender and whether or not the participant is an arranger.


#Gender and Employment

Is gender independent of currently playing in a community theater pit?
```{r echo=FALSE}
data_pit.currently$orig_gender = data_pit.currently$gender
data_pit.currently$gender = data_pit.currently$bucketed_gender
#View(data_pit.currently)
po_2 = data_pit.currently %>% mutate(pit.currently = recode(pit.currently.x,"1"="broadway","2" = "broadway.touring","3"="non.union.touring","4"="regional.theater","5"="community.theater")) %>% 
  mutate(yes_no = 1) %>%
  distinct %>%
  spread(pit.currently, yes_no, fill = 0)

po2 = po_2[!duplicated(po_2$IPAddress),]

```

```{r echo=FALSE}
#View(po2)
g_poCom= table(po2$community.theater,po2$bucketed_gender)
rownames(g_poCom) = c("No","Yes")
make_table_chi(g_poCom, "Q: Are you currently in a community theater pit?")
```

